### 2024-02-18 documentation/thesis/thesis_document.tex
.

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These holes are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~temperature sensors).

@@

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code.

It manages communication with sensors, actuators and other peripheral
devices, processing data and making decisions. Firmware is critical to
the functioning of devices.

The firmware is responsible for detecting the possible connected sensors
shown in table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
and query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.

The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. \newpage To enable the most stable
possible synchronisation between several sensors, an option has already
been created to establish an electrical connection between sensors. This
is used together with the firmware to synchronise the readout intervals.
The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors.

This means that for the subsequent readout of the measurements, it is
only important that they are taken at the same interval across all
sensors. The sensor differentiation takes place later in the
\gls{mrp}-library \ref{software-readout-framework} by using the sensor
\gls{uuid}.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6uT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets. The designed magnet holder can be
adapted for different magnet shapes and can be placed on the spacer
without backlash to be able to perform a repeatable measurement without
introducing measurement irregularities by mechanically changing the
magnet.

@@

The magnet sensor is mounted on a movable arm, which can move 180
degrees around the magnet on one axis. To be able to map the full
sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. Idal magnets are assumed at this point. However, it
should also be possible to import field data in a more measured form
later. Using the DataAquisition sub-step, it is possible to generate any
number of ideal magnets.

@@

For the host to be able to send a command to the network multi-sensor
setup, the command received needs to be forwarded to the correct sensor.
In addition, there are commands such as the previously used \emph{info}
or \emph{status} command, which must be intercepted by the
\emph{MRPProxy} module so that it can be handled differently (see
example listing \ref{lst:mtsc}).

To realize this, a \gls{lut} is created in the previous steps, which
contains information regarding \emph{requested capability}
-\textgreater{} \emph{sensor}-\gls{uuid} -\textgreater{} \emph{physical
sensor} and allows the commands to be routed.

>>>>

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These holes are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~for additional temperature sensors).

@@

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code. It manages communication with sensors,
actuators and other peripheral devices, processing data and making
decisions. Firmware is critical to the functioning of devices. The
firmware is responsible for detecting the possible connected sensors
shown in table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
and query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port.

To enable the most stable possible synchronisation between several
sensors, an option has already been created to establish an electrical
connection between sensors. This is used together with the firmware to
synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp}-library \ref{software-readout-framework} by using
the sensor \gls{uuid}.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6mT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets. The designed magnet holder can be
adapted for different magnet shapes and can be placed on the spacer
without backlash to be able to perform a repeatable measurement without
introducing measurement irregularities by mechanically changing the
magnet.

@@

The magnet sensor is mounted on a movable arm, which can move \emph{180}
degrees around the magnet on one axis. To be able to map the full
sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. Idal magnets are assumed at this point. However, it
should also be possible to import field data in a more measured form
later. Using the data aquisition sub-step, it is possible to generate
any number of ideal magnets.

@@

For the host to be able to send a command to the network multi-sensor
setup, the command received needs to be forwarded to the correct sensor.
In addition, there are commands such as the previously used \emph{info}
or \emph{status} command, which must be intercepted by the
\emph{MRPProxy} module so that it can be handled differently (see
example listing \ref{lst:mtsc}). To realize this, a \gls{lut} is created
in the previous steps, which contains information regarding
\emph{requested capability} -\textgreater{} \emph{sensor}-\gls{uuid}
-\textgreater{} \emph{physical sensor} and allows the commands to be
routed.
